The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-05-31 paper/ms.tex
paper: incorporate new plots

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf There are many clusters; TESS looks at them.} Placeholder skymap.
		\label{fig:clustermap}
	}
\end{figure*}

@@

RMS vs mag plots.

ACF statistics.

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf TESS looks at many clusters.} Placeholder skymap.
		\label{fig:clustermap}
	}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Celestial positions of light curves from Sector 6, Camera 1.}
		\label{fig:lcradec}
	}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf RMS vs mag for CDIPS light curves.}
		\label{fig:rms_vs_mag}
	}
\end{figure}

ACF statistics before and after detrending(?)
